\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{-0.530in}
% \addtolength{\evensidemargin}{-0.375in}
% \addtolength{\textwidth}{1in}
% \addtolength{\topmargin}{-.45in}
% \addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Quang Khai Lam}} & Location: Ho Chi Minh City, Vietnam\\
  \href{https://github.com/lhmqk}{Github: github.com/lhmqk} & Mobile: +84-096-8910-016 \\
  \href{https://www.linkedin.com/in/lh-mqk/}{LinkedIn: linkedin.com/in/lh-mqk/} & Email: \href{mailto:}{khai.lam2404@hcmut.edu.vn}
\end{tabular*}
\vspace{-8pt}
\begin{center}
    \parbox{4.6in}{
    \begin{center}
        I am a conscientious and enthusiastic third-year Computer Engineering student. I have strong technical skills and great interpersonal skills, enabling me to quickly adapt to any environment.
    \end{center}
    }
\end{center}
%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ho Chi Minh University of Technology}{Ho Chi Minh City, Vietnam}
      {High Quality Program - Bachelor of Computer Engineering}{Oct 2020 - Present}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Relevant Courses: }Electrical Electronic Circuits, Computer Architecture, Data Structures and Algorithms, Operating Systems, Computer Networks, Microprocessors-Microcontrollers, IoT Application Development}}}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~HTML5, CSS3, JavaScript, Python, PHP, SQL, C/C++, Assembly}
	\resumeSubItem{Frameworks}{~~~~React.js, Express.js(Node.js), Flask, Cordova, Django}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~GIT, MySQL, SQLite}
	\resumeSubItem{Platforms}{~~~~~~~Windows, Linux, Web, Arduino, Raspberry, STM32}
	\resumeSubItem{Soft Skills}{~~~~~~~Communication, Problem-Solving, Teamwork, Writing, Public Speaking, Time Management}

\resumeSubHeadingListEnd
\vspace{-5pt}
% \section{Experience}
%   \resumeSubHeadingListStart
%     \resumeSubheading{Google Summer of Code - Submitty}{Remote}
%     {Student Developer (Full-time)}{May 2019 - Sep 2019}
%     \resumeItemListStart
%         \resumeItem{Discussion Forum Upgrades}
%           {Refactor forum for performance to handle large databases.}
%           \resumeItem{REST API for Discussion Forum}
%           {Symphony \& Twig based Forum parts converted to API-first interface.}
%           \resumeItem{Ratchet PHP WebSocket}{Implemented a WebSocket for low-latency real time exchange of posts and thread updates.}
%       \resumeItemListEnd
% \vspace{-5pt}

% \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
% \vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
    \resumeSubItem{
        \begin{minipage}[t]{7.2cm}
        \flushleft
        Full-stack Blog Web Application
        \end{minipage}
        \hfill
        \begin{minipage}[t]{7cm}
        \flushright
        React.js, Node.js, MySQL | Apr 2023
        \end{minipage}
    }{
    \begin{itemize}
        \item[-]Description: A full-stack blog web app that uses React, Node.js, and MySQL. Users can create an account, log in, and create posts. The app includes user authentication, post filtering, and file upload functionality.
        \item[-]Field: Web Development.
        \item[-]Role: Full-stack Developer.
        \item[]Github: github.com/lhmqk/FullBlog
    \end{itemize}}
    \resumeSubItem{
        \begin{minipage}[t]{7.4cm}
        \flushleft
        CRUD Web System for Storage Management
        \end{minipage}
        \hfill
        \begin{minipage}[t]{7.4cm}
        \flushright
        React.js, Node.js, MySQL | Mar 2023
        \end{minipage}
    }{
    \begin{itemize}
        \item[-]Description: The utilization of Node.js and Express.js in conjunction with React.js to execute fundamental storage management operations (Create, Read, Update, Delete).
        \item[-]Field: Web Development.
        \item[-]Role: Full-stack Developer.
        \item[]Github: github.com/lhmqk/CRUD
    \end{itemize}}
    \resumeSubItem{
        \begin{minipage}[t]{7.9cm}
        \flushleft
        Smart Air Purifier System For Household Usage
        \end{minipage}
        \hfill
        \begin{minipage}[t]{6.2cm}
        \flushright
        Flask, JavaScript | Sep - Dec 2022
        \end{minipage}
    }{
    \begin{itemize}
        \item[-]Description: Implementation of an air purifier with abilities to detect temperature, humidity, PM2.5 dust and harmful gases concentration supporting with a mobile application for supervisor and control.
        \item[-]Field: Internet of Things.
        \item[-]Role: Web Server and Flask API to replace Adafruit, display and control feed's data of the system on a user-friendly Dashboard.
        \item[]Github: github.com/lhmqk/IoT\_Flask
    \end{itemize}}
\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------Languages-----------------
\section{Languages}
\begin{description}[font=$\bullet$]
\item {\textbf{Vietnamese}: Native speaker.}
\vspace{-5pt}
\item {\textbf{English}: IELTS 7.5 Certificate - Achieved in 2020.}

\end{description}

\vspace{-5pt}


\end{document}
